Update after major correction to *Management induced changes of soil organic carbon on global croplands*

### 2021-08-17 ResultNotebooks/create_LUtransition.Rmd
update LUC figure for methods

```{r arrange plot, out.height=1000 , out.width=2000}
library(cowplot)
library(ggplot2)

start     <- "../FlowFigure/LUC_start.pdf"
trans     <- "../FlowFigure/LUC_transition.pdf"
hetero    <- "../FlowFigure/LUC_hetero.pdf"
homo      <- "../FlowFigure/LUC_homo.pdf"
text      <- "../FlowFigure/LUC_text.pdf"
outputdir <- "Output/Images"

@@

grid_1 <- plot_grid(p1, p2, p3, ncol=3)
grid_2 <- plot_grid (pt, p4, ncol=2, rel_widths = c(2, 1))
grid   <- plot_grid(grid_1, grid_2, nrow=2)
grid
ggsave(paste0(outputdir,"/LUtransition.png"), plot=grid, width = 20, height = 10, dpi = 400, units = "cm", bg="white")

>>>>

```{r arrange plot, out.height=3000 , out.width=3300}
library(cowplot)
library(ggplot2)

start     <- "../FlowFigure/LUC_start_rotated.pdf"
trans     <- "../FlowFigure/LUC_transition_rotated.pdf"
hetero    <- "../FlowFigure/LUC_hetero_rotated.pdf"
homo      <- "../FlowFigure/LUC_homo_rotated.pdf"
text      <- "../FlowFigure/LUC_text_rotated.pdf"
outputdir <- "Output/Images"

@@

grid_1 <- plot_grid(p1, p2, p3, ncol=3)
grid_2 <- plot_grid (pt, p4, ncol=2, rel_widths = c(2, 1))
grid   <- plot_grid(grid_1, grid_2, nrow=2)
grid
ggsave(paste0(outputdir,"/LUtransition_rotated.png"), plot=grid, width = 33, height = 30, dpi = 400, units = "cm", bg="white")
